---
title: "ryx-overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ryx-overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction
The `ryx` package simplifies correlation analysis by providing tools to calculate and visualize correlations between a target variable and multiple predictors.

## Installation
To install the development version of `ryx`, use:
```{r}
#devtools::install_github("braedenfalzarano/ryx")
```


## Example Usage
Here’s a quick guide to using ryx:
```{r}
# library(ryx)
# library(MASS)
# 
# # Perform correlation analysis
# x <- ryx(Boston, y = "medv")
# 
# # Print results
# print(x)
# 
# # Summary of results
# summary(x)
# 
# # Plot results
# plot(x)
```

## Details
The ryx function calculates Pearson correlations and arranges them in a data frame. The summary method provides a statistical overview, and the plot method visualizes the results.

## Conclusion
The ryx package streamlines correlation analysis, making it quick and easy to generate insights.



